NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PS lipids

### 2018-06-28 Manuscript/manuscriptPS.tex
Add preliminary version of conclusions section

\begin{table*}[!htb]
%\begin{sidewaystable*}[!p]
\centering
\caption{  List of MD simulations. The salt concentrations calculated as 
   [salt]=N$_{\rm c} \times$[water]\,/\,N$_{\rm w}$, where [water]\,=\,55.5~M.
   CKPM refers to the version with Berger/Chiu NH$_3$ charges compatible with Berger
   (i.e. the NH$_3$ group having the same charges as in the N(CH$_3$)$_3$ group of the PC lipids;
   'M' stands for Mukhopadhyay after the first published Berger-based PS simulation that used these charges \cite{??})
   and CKP refers to the version with more Gromos compatible version
   (i.e. the charges for the NH$_3$ group taken from the lysine side-chain).
   %   these correspond the concentrations reported in the experiments by Akutsu et al.~\cite{akutsu81}.
   %   The lipid force fields named as in our previous work~\cite{botan15}.
}\label{IONsystems}
%begin{minipage}[t]{\textwidth}
\begin{tabular}{l c c r r r r r r c c}
  lipid/counter-ions & force field for lipids / ions & NaCl (mM) & CaCl$_2$\,(mM) &  \footnote{Number of lipid molecules with largest mole fraction}N$_{\rm l}$   &  \footnote{Number of water molecules}N$_{\rm w}$ \todoi{Should confirm that the amounts of water in experiments matched those in simulations.}   & \footnote{Number of additional cations}N$_{\rm c}$  & \footnote{Simulation temperature}T (K)  & \footnote{Total simulation time}t$_{{\rm sim}}$(ns) & \footnote{Time used for analysis}t$_{{\rm anal}}$ (ns) &   \footnote{Reference for simulation files}files\\
  \hline
    POPC:POPS (5:1)/K$^+$  & CHARMM36 \cite{klauda10,venable13} &0 & 0  & 110:22 & 4935 & 0  & 298  & 100 & 100 \todoi{Equilibration?} & \cite{charmm36pops+83popcT298K}  \\
    POPC:POPS (5:1)/K$^+$  & CHARMM36 \cite{klauda10,venable13}          &0 & 0 & 250:50 & ?     & 0  & 298  & 200 & ?   & \cite{??} \todoi{Trajectories and further details to be added by J. Madsen}  \\
    POPC:POPS (5:1)/K$^+$  & CHARMM36 \cite{klauda10,venable13}          &0 & 0 & 110:22 & 4620  & 0  & 298  & 500 & 100 & \cite{charmm36pops+83popcT298Kpiggot}  \\
    POPC:POPS (5:1)/Na$^+$ & CHARMM36 \cite{klauda10,venable13}          &0 & 0 & 110:22 & 4620  & 0  & 298  & 500 & 100 & \cite{charmm36pops+83popcT298KpiggotSODIUM}  \\
    POPC:POPS (1:1)/K$^+$  & CHARMM36 \cite{klauda10,venable13}          &0 & 0 & 150:150 & ?    & 0  & 298  & 200 & ?   & \cite{??} \todoi{Trajectories and further details to be added by J. Madsen}  \\
     POPC:POPS (5:1)        & CHARMM36 \cite{klauda10,venable13,kim16}   &0 & 150 \todoi{Concentration to be checked} & 250:50 & ?  & ?  & 298  & 200 & ?  & \cite{??} \todoi{Trajectories and further details to be added by J. Madsen}  \\
    POPC:POPS (5:1)        & CHARMM36 \cite{klauda10,venable13,kim16}    &0 & 1000 \todoi{Concentration to be checked} & 250:50 & ?  & ?  & 298  & 200 & ?  & \cite{??} \todoi{Trajectories and further details to be added by J. Madsen}  \\
    \hline
    POPC:POPS\todoi{This is also probably OPPS? These should be corrected in this table as well.} (5:1)/K$^+$  & MacRog \cite{maciejewski14} &0 & 0  & 120:24 & 5760 & 0  & 298  & 200 & 200 \todoi{Equilibration?} & \cite{POPCpopsMACROG}  \\
   POPC:POPS (5:1)/K$^+$  & MacRog \cite{maciejewski14} &0 &100 & 120:24 & 5760 & 10  & 298  & 200 & 200 \todoi{Equilibration?} & \cite{POPCpopsMACROG}  \\
    POPC:POPS (5:1)/K$^+$  & MacRog \cite{maciejewski14} &0 &300 & 120:24 & 5760 & 31  & 298  & 200 & 200 \todoi{Equilibration?} & \cite{POPCpopsMACROG}  \\
    POPC:POPS (5:1)/K$^+$  & MacRog \cite{maciejewski14} &0 &1000 & 120:24 & 5760 & 104  & 298  & 200 & 200 \todoi{Equilibration?} & \cite{POPCpopsMACROG}  \\
    POPC:POPS (5:1)/K$^+$  & MacRog \cite{maciejewski14} &0 &3000 & 120:24 & 5760 & 311  & 298  & 200 & 200 \todoi{Equilibration?} & \cite{POPCpopsMACROG}  \\
    \todo{MacRog simulations with KCl to be added}\\
    \hline
    \todo{Berger simulations with NaCl and CaCl to be added}
\end{tabular}
%\end{minipage}
%\end{sidewaystable*}

@@

\section{Conclusions}

>>>>

\begin{table*}[!htb]
%\begin{sidewaystable*}[!p]
\centering
\caption{  List of MD simulations. The salt concentrations calculated as 
   [salt]=N$_{\rm c} \times$[water]\,/\,N$_{\rm w}$, where [water]\,=\,55.5~M.
   CKPM refers to the version with Berger/Chiu NH$_3$ charges compatible with Berger
   (i.e. the NH$_3$ group having the same charges as in the N(CH$_3$)$_3$ group of the PC lipids;
   'M' stands for Mukhopadhyay after the first published Berger-based PS simulation that used these charges \cite{??})
   and CKP refers to the version with more Gromos compatible version
   (i.e. the charges for the NH$_3$ group taken from the lysine side-chain).
   %   these correspond the concentrations reported in the experiments by Akutsu et al.~\cite{akutsu81}.
   %   The lipid force fields named as in our previous work~\cite{botan15}.
}\label{IONsystems}
    \todo{Berger simulations with NaCl and CaCl to be added}
%begin{minipage}[t]{\textwidth}
\begin{tabular}{l c c r r r r r r c c}
  lipid/counter-ions & force field for lipids / ions & NaCl (mM) & CaCl$_2$\,(mM) &  \footnote{Number of lipid molecules with largest mole fraction}N$_{\rm l}$   &  \footnote{Number of water molecules}N$_{\rm w}$ \todoi{Should confirm that the amounts of water in experiments matched those in simulations.}   & \footnote{Number of additional cations}N$_{\rm c}$  & \footnote{Simulation temperature}T (K)  & \footnote{Total simulation time}t$_{{\rm sim}}$(ns) & \footnote{Time used for analysis}t$_{{\rm anal}}$ (ns) &   \footnote{Reference for simulation files}files\\
  \hline
    POPC:POPS (5:1)/K$^+$  & CHARMM36 \cite{klauda10,venable13} &0 & 0  & 110:22 & 4935 & 0  & 298  & 100 & 100 \todoi{Equilibration?} & \cite{charmm36pops+83popcT298K}  \\
    POPC:POPS (5:1)/K$^+$  & CHARMM36 \cite{klauda10,venable13}          &0 & 0 & 250:50 & ?     & 0  & 298  & 200 & ?   & \cite{??} \todoi{Trajectories and further details to be added by J. Madsen}  \\
    POPC:POPS (5:1)/K$^+$  & CHARMM36 \cite{klauda10,venable13}          &0 & 0 & 110:22 & 4620  & 0  & 298  & 500 & 100 & \cite{charmm36pops+83popcT298Kpiggot}  \\
    POPC:POPS (5:1)/Na$^+$ & CHARMM36 \cite{klauda10,venable13}          &0 & 0 & 110:22 & 4620  & 0  & 298  & 500 & 100 & \cite{charmm36pops+83popcT298KpiggotSODIUM}  \\
    POPC:POPS (1:1)/K$^+$  & CHARMM36 \cite{klauda10,venable13}          &0 & 0 & 150:150 & ?    & 0  & 298  & 200 & ?   & \cite{??} \todoi{Trajectories and further details to be added by J. Madsen}  \\
     POPC:POPS (5:1)        & CHARMM36 \cite{klauda10,venable13,kim16}   &0 & 150 \todoi{Concentration to be checked} & 250:50 & ?  & ?  & 298  & 200 & ?  & \cite{??} \todoi{Trajectories and further details to be added by J. Madsen}  \\
    POPC:POPS (5:1)        & CHARMM36 \cite{klauda10,venable13,kim16}    &0 & 1000 \todoi{Concentration to be checked} & 250:50 & ?  & ?  & 298  & 200 & ?  & \cite{??} \todoi{Trajectories and further details to be added by J. Madsen}  \\
    \hline
    POPC:POPS\todoi{This is also probably OPPS? These should be corrected in this table as well.} (5:1)/K$^+$  & MacRog \cite{maciejewski14} &0 & 0  & 120:24 & 5760 & 0  & 298  & 200 & 200 \todoi{Equilibration?} & \cite{POPCpopsMACROG}  \\
   POPC:POPS (5:1)/K$^+$  & MacRog \cite{maciejewski14} &0 &100 & 120:24 & 5760 & 10  & 298  & 200 & 200 \todoi{Equilibration?} & \cite{POPCpopsMACROG}  \\
    POPC:POPS (5:1)/K$^+$  & MacRog \cite{maciejewski14} &0 &300 & 120:24 & 5760 & 31  & 298  & 200 & 200 \todoi{Equilibration?} & \cite{POPCpopsMACROG}  \\
    POPC:POPS (5:1)/K$^+$  & MacRog \cite{maciejewski14} &0 &1000 & 120:24 & 5760 & 104  & 298  & 200 & 200 \todoi{Equilibration?} & \cite{POPCpopsMACROG}  \\
    POPC:POPS (5:1)/K$^+$  & MacRog \cite{maciejewski14} &0 &3000 & 120:24 & 5760 & 311  & 298  & 200 & 200 \todoi{Equilibration?} & \cite{POPCpopsMACROG}  \\
    \hline
\end{tabular}
%\end{minipage}
%\end{sidewaystable*}

@@

\section{Conclusions}
We have collected a set of experimental NMR order parameter data,
which could be combined with MD simulations to interpret the
headgroup structure and cation binding details to negatively charged
membranes containing PS lipids. Using open collaboration method, we
tried to find a MD simulation model which would be sufficiently accurate
to interpret the experimental data. However, none of the tested models
was accurate enough. In line with the previous study for PC lipids \cite{catte16},
MD simulation models seems to generally overestimate cation binding also
to negatively charged bilayers containing PS lipids, with some exceptions.
The response of PS lipid headgroup order parameters to the bound cations
does not agree with experiments, even in the cases where binding affinity is
not overestimated. This is in contrast to the previous results with PC lipids,
where the qualitative response of the headgroup order parameters was in agreement
with experiments even in the cases where the headgroup structure without ions was not
correct and the cation binding affinity was overestimated. In addition, the inaccurate
responses of PS headgroup order parameters to the dilution with PC lipids suggests
that the PC-PS interactions are not accurately described by the tested models.

Our results pave the way for improving the PS lipid parameters for MD simulations
by offering the set of experimental data for the quality measurement, by
pinpointing problems areas in the models and suggesting directions for the corrections.
Improvements using the electronic continuum correction is already in progress \url{https://github.com/jmelcr/ecc_lipids},
following the recent work for PC lipids \cite{melcr18}.
